On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-21 docs/mvfits_paper/mvf.tex
resutructuring draft to include appendix
fixing typo; adding to doc and paper

@@

\end{table}
%
%
\par In this example case, \gmvr{} correctly recovers the functional form of the input data. But, in general, \gmvr{} and related techniques, having no knowledge of , will attempt to model minor correlations and offsets within the training data's noise.
%
However, we have demonstrated the utility of \gmvr{} in a relatively ideal usage case where the underlying function is rational, and the training data is inly weakly contaminated with noise.
%
In the following sections, we consider cases where the functional form of the sample data is not known to be explicitly rational, but the amount of noise within the training data is negligible.
%
%
\begin{figure*}
  %
  \includegraphics[width=\textwidth]{fig/issue3_summary.pdf}
  %
	\caption{ Standard summary plot for \gmvr. }
  %
  \label{fig:gmvrtoy}
  %
\end{figure*}

@@

% Plots of QNM frequencies
\begin{figure*}
  \begin{tabular}{lcr}
    \includegraphics[width=\figfactor\textwidth]{fig/fits_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/fits_tau.pdf}
	\caption{ Fits of dimensionless \qnm{} central frequencies (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
  Before the application of $\kappa(\j{})$, points are spaced between -\CwFitCalibrationRegion and \CwFitCalibrationRegion according to \CwFitCalibrationRegion times the $\sin$ of a fiducial angle which is uniformly spaced between $-\pi/2$ and $\pi/2$. Values of $\j{}$ are shown in the upper axis for $\kappa$ at $l=m$.
  The grey dashed line marks the value of $\kappa$ where $\j{}=0$. Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. }
  \label{fig:qnms}
% Plots of QNM frequencies
\begin{figure*}
  \begin{tabular}{lcr}
    \includegraphics[width=\figfactor\textwidth]{fig/res_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/res_tau.pdf}
	\caption{ Fractional residual errors for fits of dimensionless \qnm{} central frequencies and decay times (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. }
  \label{fig:qnm_err}

@@

\par While it is possible to enforce extremal Kerr conditions $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for all $\sigma_{\LMlmn}$, and then apply this form to the modeling of all $\sigma_{\LMlmn}$.

@@

% \par \eqns{}

@@

% Equations for mixing coefficients
  \input{src/ysprod_eqns}

% Plots of mixing coefficients
\begin{figure*}
  %
  \begin{tabular}{lcr}
    \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_2.pdf}
  \end{tabular}
  %
	\caption{ Spherical-spheroidal harmonic mixing coefficients. }
  %
\end{figure*}

% Plots of mixing coefficients
\begin{figure*}
  %
  \begin{tabular}{lcr}
    \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_3.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_4.pdf}
  \end{tabular}
  %
	\caption{ Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models. }
  %
\end{figure*}

@@

>>>>

\begin{figure*}[htb]
  \includegraphics[width=\textwidth]{fig/issue3_summary.pdf}
	\caption{ Standard summary plot for \gmvr. }
  \label{fig:gmvrtoy}

@@

\end{table}
%
%
\par In this example case, \gmvr{} correctly recovers the functional form of the input data. But, in general, \gmvr{} and related techniques, having no knowledge of , will attempt to model minor correlations and offsets within the training data's noise.
%
However, we have demonstrated the utility of \gmvr{} in a relatively ideal usage case where the underlying function is rational, and the training data is inly weakly contaminated with noise.
%
In the following sections, we consider cases where the functional form of the sample data is not known to be explicitly rational, but the amount of noise within the training data is negligible.

@@

@@

\par While it is possible to enforce extremal Kerr and Schwarzschild limiting conditions for $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for all $\sigma_{\LMlmn}$, and then apply this form to the modeling of all $\sigma_{\LMlmn}$.

@@

\eqns{eq:ys22220}{eq:ys55550} present the resulting model equations.

@@

\fig{fig:ys} display comparisons of the fits with training data as well as related residuals.
For efficiency of presentation, each $\sigma_{\LMlmn}$ is plotted against its real and imaginary part.
In cases where $(\bar\ell,\bar{m})=(\ell,m)$, the real part of $\sigma_{\LMlmn}$ varies about unity in a manner consistent with the Schwarzschild limit, where $\sigma_{\LMlmn}=\delta_{\bar\ell}^{\ell}\;\delta_{\bar{m}}^{m}$.
This is equally true in cases where $(\bar\ell,\bar{m}) \neq (\ell,m)$.
As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent.

@@

%
\appendix

\section{Algorithms}
\label{app:algos}

% \begin{widetext}
% \hspace{1cm}
% \hspace{1cm}
% \hspace{1cm}
% \hspace{1cm}

% \end{widetext}

\section{Equations}
\label{app:eqns}

%
% Equations for mixing coefficients
%
\begin{widetext}
  \input{src/ysprod_eqns}
\end{widetext}

\section{Figures}
\label{app:figs}

%
% Plots of QNM frequencies
\begin{figure*}
  %
  \begin{tabular}{lr}
    \includegraphics[width=\figfactor\textwidth]{fig/fits_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/fits_tau.pdf}
    \\
    \includegraphics[width=\figfactor\textwidth]{fig/res_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/res_tau.pdf}
  \end{tabular}
  %
	\caption{ Fits of dimensionless \qnm{} central frequencies (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
  %
  Before the application of $\kappa(\j{})$, points are spaced between -\CwFitCalibrationRegion and \CwFitCalibrationRegion according to \CwFitCalibrationRegion times the $\sin$ of a fiducial angle which is uniformly spaced between $-\pi/2$ and $\pi/2$. Values of $\j{}$ are shown in the upper axis for $\kappa$ at $l=m$.
  %
  The grey dashed line marks the value of $\kappa$ where $\j{}=0$. Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. (Bottom) Percentage residual errors for fits of dimensionless \qnm{} central frequencies and decay times (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. }
  %
  \label{fig:qnm}
  %
\end{figure*}

% Plots of mixing coefficients
\begin{figure*}
  %
  \begin{tabular}{lr}
    \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_2.pdf} \\
    \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_3.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_4.pdf}
  \end{tabular}
  %
	\caption{ Spherical-spheroidal harmonic mixing coefficients. Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models. }
  %
  \label{fig:ys}
  %
\end{figure*}
